Stratified Random Sampling
```{r}
library(caret)
data(spam)
spam = spam
dim(spam)
str(spam)
prop.table(table(spam$type))
mean(spam$all)
```
##### "Spam"" takes about 40% of the total types  
##### Overall "all" is 0.28  
##### We want out train and test set to keep the same proportion/mean on these two features  
##### We will use createDataPartition and pass the features we want to stratify  

```{r}
ind = createDataPartition(c(spam$type,spam$all),p=0.5,list=F)
spam_trn = spam[ind,]
prop.table(table(spam_trn$type))
mean(spam_trn$all,na.rm=T)
spam_tst = spam[-ind,]
prop.table(table(spam_tst$type))
mean(spam_tst$all)
```

##### We can conclude that the same proportion/mean are generated for the train and test set

SMOTE
---
##### SMOTE: Synthetic Minority Over-sampling Techniques  
##### rare events: <15% target variables, imbalanced, SMOTE can help oversample the dataset. It uses bootstrapping and k-nearest neighbors and synthetically create more observations

```{r}
library(DMwR)
SMOTE
```
- perc.over = k, how much you want to oversample  
- perc.under = k, how much you want to undersample

